

```{r,echo = TRUE}
text <- "Text mining usually involves the process of structuring
the input text. The overarching goal is, essentially, to turn text 
into data for analysis, via application of natural language processing (NLP) 
and analytical methods."

# Load qdap
library(qdap)

# Find the 10 most frequent terms: term_count
term_count <- freq_terms(text, 10)

# Plot term_count
plot(term_count)
```
Text mining begins with loading some text data into R, which we'll do with the read.csv() function. By default, read.csv() treats character strings as factor levels like Male/Female. To prevent this from happening, it's very important to use the argument stringsAsFactors = FALSE.

A best practice is to examine the object you read in to make sure you know which column(s) are important. The str() function provides an efficient way of doing this. You can also count the number of documents using the nrow() function on the new object. In this example, it will tell you how many coffee tweets are in the vector.

If the data frame contains columns that are not text, you may want to make a new object using only the correct column of text (e.g. some_object$column_name). 

```{r,echo = TRUE}
# Import text data
tweets <- read.csv('coffee.csv', stringsAsFactors = F)

# View the structure of tweets
str(tweets)

# Print out the number of rows in tweets
nrow(tweets)

# Isolate text from tweets: coffee_tweets
coffee_tweets <- tweets$text
```
```{r, echo = TRUE}
# Create the object: text
text <- "<b>She</b> woke up at       6 A.M. It\'s so early!  She was only 10% awake and began drinking coffee in front of her computer."

# All lowercase
tolower(text)

# Remove punctuation
removePunctuation(text)

# Remove numbers
removeNumbers(text)

# Remove whitespace
stripWhitespace(text)

# Remove text within brackets
bracketX(text)

# Replace numbers with words
replace_number(text)

# Replace abbreviations
replace_abbreviation(text)

# Replace contractions
replace_contraction(text)

# Replace symbols with words
replace_symbol(text)
```
